\section{Related Work}
\label{section:relatedwork}
While there have been a number of works in automating outfit selection, they are all geared towards
fashion selection either for aesthetics or occasions (e.g. wedding, funeral, interview, or church).
There does not seem to be any existing work in the climate-outfitting field, let alone with an
activity focus.

In general, related works fall into three categories: fashionable outfit selection, category-based
outfit selection, and general temperature/climate automation. Here several related works are briefly introduced:

\subsection{Fashionable Outfit Selection}
\cite{Dressup} uses a wardrobe of known clothes to suggest outfits based on the user's appearance.
Of note is that outfits are suggested based on a dress code constraint, which is a similar task to
the challenge of outfit selection.

\cite{SmartCloset} works on outfit selection and sharing, focused on comparing and lending wardrobe
to others. There may be some similarities between this and the idea of comparing user outfit preferences
for Gear Smarts.

\cite{MagicCloset} used Amazon's mechanical turks to fill a database of available-to-purchase outfits.
Using this dataset, they constructed an occasion-oriented outfit suggestion tool similar to \cite{Dressup}.

\cite{ThermalComfort} discusses a new approach to thermal control of homes. This could relate well to
adapting Gear Smarts to sub-activities with different thermal properties (e.g. mogul vs groomer skiing).

\subsection{Machine Learning Technique Selection}
There are numerous papers discussing and comparing the various options for machine learning techniques.
Some relevant papers to the decision of which technique to use for Gear Smarts include \cite{ML:MapReduceClusters},
\cite{ML:ManufacturingSystems}, \cite{ML:IPTraffic}, and \cite{ML:GeoMapping}.
